Trends of SDR in Thessaloniki

### 2023-10-24 Article.Rmd
Commit 2023-10-24 16:14

```{r SZAtrendSeason, echo = FALSE, fig.cap='SDR trend ~ SZA', out.width='100%'}
knitr::include_graphics("./images/SzaTrendsSeasTogether-2.png")
```

>>>>

```{r SZAtrendSeason, echo = FALSE, fig.cap='Seasonla distribution of the SDR\'s long term trends by SZA before and after noon. The solid data points represent values with an acceptable statistical significance ($p<0.005$), the trends were computed with SZA bins of $1^\\circ$ for each day, before and after local noon, all graphs have the same scale. Bins with $p<0.005$ or with less than 85 data points may be missing from the view.', out.width='100%'}
knitr::include_graphics("./images/SzaTrendsSeasTogether-2.png")
```
